Does online masked priming pass the test?\\ The effects of prime exposure duration on masked identity priming

### 2021-11-03 previous revisions/MaskedPriming_complete_mspg.tex
Move old documents to different directory, make final Rmd and tex files

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Online masked priming}
\keywords{Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration\newline\indent Word count: 7916}
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Fortunately, in recent years, there have been significant improvements in how content can be presented on the World Wide Web. Most notably, the HTML5 standard now makes it possible to use Javascript in order to draw stimuli interactively and monitor participant responses with remarkable flexibility inside the browser. Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets (Reimers \& Stewart, 2015). There have been attempts to use this technology for online masked priming experiments: Crump et al. (2013) (Experiment 7) attempted a masked priming paradigm using custom written Javascript code, but failed to replicate the masked priming effect which may be due to problems with their implementation (unfortunately, their study does not provide many details about the Javascript code used). Barnhoorn et al. (2015) developed a software package called \emph{QRTEngine} designed to run experiments within the Qualtrics online survey development environment (Qualtrics, 2020) and were able to successfully find masked priming effects (Experiment 3). Unfortunately, \emph{QRTEngine} was only maintained for a few years and is now defunct, which is an issue with many custom-developed solutions.

Nowadays, there a variety of well-maintained software packages taking advantage of the HTML5 capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla (Anwyl-Irvine, Massonni, et al., 2020) or Testable (Rezlescu et al., 2020), and open-source such as jsPsych (de Leeuw, 2015) or PsychoJS (the Javascript version of PsychoPy 3, Peirce et al., 2019). In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds. Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility of recruiting participants for on-line experiments based on various specific characteristics set up by the experimenters regardless of their location (e.g., native French speakers, not older than 30 years old, not currently in college).

@@

All in all, replicating the results observed in controlled laboratory masked priming studies would be an important step in establishing the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli (e.g., Parker et al., 2021). This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms Ratcliff \& Hendrickson (2021). So far, this has only been possible in many-labs studies depending on the collaboration of many researchers in different countries (e.g., Adelman et al., 2014). Importantly, the present experiments go beyond an online replication: they allow us to test masked priming effects not only across conditions (identity vs.~unrelated) but also within conditions (the effect of identity primes, or unrelated primes, across two prime durations) (see Jacobs et al., 1995; Ziegler et al., 2000, for advantages of within-condition comparisons). Thus, the within-subject manipulation of prime exposure duration in both experiments allows us to obtain a comprehensive picture of masked identity priming effects--also including the examination of potential inhibitory effects of unrelated primes.

@@

\begin{figure}
\centering
\includegraphics{MaskedPriming_revision_files/figure-latex/hyp-mod-dat-figure-1.pdf}
\caption{\label{fig:hyp-mod-dat-figure}Mapping from hypotheses to data via evidence accumulation models. The bottom part of each graph represents sample paths, and the top part shows the cumulative density functions. From left to right: \emph{Null Effect} - there are no differences between the conditions; \emph{Effect in Encoding} - the difference between the conditions is on the encoding time, hence the RT distributions are shifted; and \emph{Effect of Encoding and Evidence Accumulation} - the differences between the conditions is on the rate of evidence accumulation, thus increasing the effect size for longer RTs (right-tail of the distribution).}
\end{figure}

@@

The pre-registration form for Experiment 1 can be found at \url{https://osf.io/v97bp}, and the materials, data files, and R scripts can be found at \url{https://osf.io/57rzq/}.

@@

We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R (Version 4.1.1; R Core Team, 2021) and the R-packages \emph{bayestestR} (Version 0.11.0; Makowski et al., 2019), \emph{brms} (Version 2.16.1; Bürkner, 2017, 2018), \emph{dplyr} (Version 1.0.7; Wickham et al., 2021), \emph{forcats} (Version 0.5.1; Wickham, 2021a), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{papaja} (Version 0.1.0.9997; Aust \& Barth, 2020), \emph{patchwork} (Version 1.1.1; Pedersen, 2020), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{Rcpp} (Eddelbuettel \& Balamuta, 2018; Version 1.0.7; Eddelbuettel \& François, 2011), \emph{readr} (Version 2.0.1; Wickham \& Hester, 2020), \emph{readxl} (Version 1.3.1; Wickham \& Bryan, 2019), \emph{rworldmap} (Version 1.3.6; South, 2011), \emph{see} (Version 0.6.7; Lüdecke et al., 2020), \emph{sp} (Version 1.4.5; Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.4; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.1.3; Wickham, 2021b), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.1; Barth, 2021), and \emph{xfun} (Version 0.26; Xie, 2021).}. We only analyzed trials where the target stimulus was a word. For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as incorrect responses (5.84 \% of trials). For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (0.36 \% of trials). For both RTs and accuracy, we fitted a model with priming condition (unrelated vs.~identical) and prime duration (33.3 ms vs.~50 ms) as well as their interaction as the fixed effects. For the discrete predictors, we used contrasts as follows: For priming condition, identical was coded as -0.5 and unrelated was coded as 0.5. For priming duration, 33.3 ms was coded as -0.5 and 50 ms was coded as 0.5. We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items. We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component \(\mu\) and the scale parameter of the exponential component \(\beta\) (equaling the inverse of the rate parameter \(\lambda\)) being allowed to vary between conditions. To model response accuracy, we used the Bernoulli distribution with a logit link. We used the default priors suggested by \emph{brms} except for the coefficients for the fixed effects, for which we applied weakly informative priors of \(\beta \sim N(0,100)\) in order to rule out improbably large effect sizes. Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations (10,000 iterations with 2000 warm-up iterations for the accuracy models). We consider an effect as credible if the 95\% Credible Interval (CrI) estimated from the posterior distribution does not contain zero. In addition, to better visualize the distributional features of the latency data, we computed the delta plots for both priming and prime duration effects.

@@

\begin{tabular}{lllllllll}
\toprule
Stimulus Type & \multicolumn{1}{c}{Prime Duration} & \multicolumn{1}{c}{Relatedness} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Accuracy}\\
\midrule
Nonword & 33.3 ms & Identity & 700 & 665 & 187 & 263 & 1,776 & 0.91\\
Nonword & 33.3 ms & Unrelated & 702 & 664 & 188 & 256 & 1,770 & 0.92\\
Nonword & 50 ms & Identity & 700 & 658 & 189 & 256 & 1,760 & 0.91\\
Nonword & 50 ms & Unrelated & 699 & 657 & 185 & 251 & 1,796 & 0.93\\
Word & 33.3 ms & Identity & 630 & 599 & 164 & 254 & 1,796 & 0.94\\
Word & 33.3 ms & Unrelated & 652 & 619 & 166 & 254 & 1,783 & 0.93\\
Word & 50 ms & Identity & 608 & 575 & 161 & 265 & 1,784 & 0.96\\
Word & 50 ms & Unrelated & 649 & 620 & 158 & 294 & 1,710 & 0.93\\
\bottomrule
\end{tabular}

@@

The RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 31.55, 95\% CrI {[}27.16, 35.92{]}), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (\emph{b} = -10.96, 95\% CrI {[}-14.83, -7.11{]}). The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = 19.31, 95\% CrI {[}11.39, 27.09{]}). The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.01, 0.07{]}). However, the 50 ms prime exposure duration seems to be associated with a slightly lower \(\beta\), i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition (\emph{b} = -0.07, 95\% CrI {[}-0.12, -0.03{]}). On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (\emph{b} = 0.03, 95\% CrI {[}-0.05, 0.12{]}).

@@

\begin{tabular}{cccccc}
\toprule
Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
\midrule
Intercept ($\mu$) & 633.707 & 8.815 & 617.142 & 651.175 & 1.006\\
Intercept ($\beta$) & 4.686 & 0.042 & 4.601 & 4.768 & 1.001\\
Relatedness ($\mu$) & 31.551 & 2.228 & 27.162 & 35.915 & 1.000\\
Prime Duration ($\mu$) & -10.959 & 1.947 & -14.825 & -7.105 & 1.000\\
Relatedness:Prime Duration ($\mu$) & 19.306 & 4.026 & 11.388 & 27.094 & 1.000\\
Relatedness ($\beta$) & 0.031 & 0.022 & -0.011 & 0.073 & 1.000\\
Prime Duration ($\beta$) & -0.074 & 0.024 & -0.120 & -0.028 & 1.000\\
Relatedness:Prime Duration ($\beta$) & 0.031 & 0.042 & -0.051 & 0.115 & 1.000\\
\bottomrule
\addlinespace
\end{tabular}

@@

\begin{figure}
\centering
\includegraphics{MaskedPriming_revision_files/figure-latex/deltas-e1-words-1.pdf}
\caption{\label{fig:deltas-e1-words}Delta plots depicting the magnitude of the effect over time in Experiment 1. Each dot represents the mean RT at the .1, .3, .5, .7 and .9 quantiles. \emph{Panel A)} Difference in RT between unrelated and related trials for the 33.3 ms prime duration (left) and the 50 ms prime duration (right). \emph{Panel B)} Difference in RT between 50 ms and 33.3 ms prime duration trials for the identity (right) and the unrelated (left) conditions.}
\end{figure}

@@

The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (\emph{b} = -0.50, 95\% CrI {[}-0.72, -0.31{]}). The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33.3 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (\emph{b} = 0.19, 95\% CrI {[}-0.02, 0.42{]}). The interaction term indicates that the effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = -0.53, 95\% CrI {[}-0.94, -0.14{]}).

@@

\begin{tabular}{cccccc}
\toprule
Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
\midrule
Intercept & 3.458 & 0.122 & 3.224 & 3.705 & 1.000\\
Relatedness & -0.503 & 0.105 & -0.720 & -0.305 & 1.000\\
Prime Duration & 0.192 & 0.110 & -0.016 & 0.417 & 1.000\\
Relatedness:Prime Duration & -0.530 & 0.206 & -0.944 & -0.138 & 1.000\\
\bottomrule
\end{tabular}

@@

We analyzed the data in the same way as in Experiment 1, by only analyzing trials where the target stimulus was a word. For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms or higher than 1800 ms as well as those with incorrect responses (4.93 \% of trials). For the accuracy analysis, we only excluded trials with RTs lower than 250 ms or higher than 1800 ms (0.15 \% of trials). For priming duration, 16.7 ms was coded as -0.5 and 33.3 ms was coded as 0.5. Otherwise, the model specifications were identical to those in Experiment 1.

@@

As in Experiment 1, the RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 8.53, 95\% CrI {[}5.07, 12.11{]}). For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (\emph{b} = -3.60, 95\% CrI {[}-7.22, -0.03{]}). However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (\emph{b} = 15.17, 95\% CrI {[}8.52, 21.73{]}). The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.02, 0.07{]}), prime exposure duration (\emph{b} = 0.01, 95\% CrI {[}-0.03, 0.05{]}), or their interaction (\emph{b} = -0.03, 95\% CrI {[}-0.12, 0.05{]}), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.

@@

\begin{tabular}{cccccc}
\toprule
Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
\midrule
Intercept ($\mu$) & 656.975 & 9.036 & 639.056 & 674.711 & 1.003\\
Intercept ($\beta$) & 4.658 & 0.043 & 4.573 & 4.741 & 1.003\\
Relatedness ($\mu$) & 8.529 & 1.795 & 5.065 & 12.106 & 1.000\\
Prime Duration ($\mu$) & -3.602 & 1.813 & -7.216 & -0.033 & 1.000\\
Relatedness:Prime Duration ($\mu$) & 15.166 & 3.390 & 8.517 & 21.727 & 1.000\\
Relatedness ($\beta$) & 0.028 & 0.023 & -0.016 & 0.073 & 1.000\\
Prime Duration ($\beta$) & 0.011 & 0.021 & -0.031 & 0.053 & 1.000\\
Relatedness:Prime Duration ($\beta$) & -0.034 & 0.043 & -0.119 & 0.049 & 1.000\\
\bottomrule
\addlinespace
\end{tabular}

>>>>

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Online masked priming}
\keywords{Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration\newline\indent Word count: 8051}
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Fortunately, in recent years, there have been significant improvements in how content can be presented on the World Wide Web. Most notably, the HTML5 standard now makes it possible to use Javascript in order to draw stimuli interactively and monitor participant responses with remarkable flexibility inside the browser. Participants do not have to install any software, and the HTML5 standard is supported by a wide variety of devices, including mobile phones and tablets (Reimers \& Stewart, 2015). There is now a variety of software packages taking advantage of the new capabilities to present experimental stimuli and collect data, both commercial, such as Gorilla (Anwyl-Irvine, Massonni, et al., 2020) or Testable (Rezlescu et al., 2020), and open-source such as jsPsych (de Leeuw, 2015) or PsychoJS (the Javascript version of PsychoPy 3, Peirce et al., 2019). In addition, online setups allow researchers to target any individual with an internet connection as a participant, from very different countries and backgrounds. Indeed, various on-line platforms (e.g., Prolific, Amazon Mechanical Turk) offer the possibility of recruiting participants for on-line experiments based on various specific characteristics set up by the experimenters regardless of their location (e.g., native French speakers, not older than 30 years old, not currently in college).

@@

All in all, replicating the results observed in controlled laboratory masked priming studies would be an important step in establishing the validity of online masked priming tasks, even in a scenario with no control over many variables (e.g., the devices in which the experiment is run, the level of contrast of the computer screen, or the additional applications that are running in the background of said device), as has been done with other paradigms that also require a high control of the presentation timing and location of the stimuli (e.g., Parker et al., 2021). This would open the possibility for masked priming researchers to collect large samples from diverse populations via online crowdsourcing methods, as has been done previously using other paradigms (e.g., Aguasvivas et al., 2020; Brysbaert et al., 2021; Brysbaert et al., 2016; Mandera et al., 2020). So far, this has only been possible in many-labs studies depending on the collaboration of many researchers in different countries (e.g., Adelman et al., 2014). Importantly, the present experiments go beyond an online replication: they allow us to test masked priming effects not only across conditions (identity vs.~unrelated) but also within conditions (the effect of identity primes, or unrelated primes, across two prime durations) (see Jacobs et al., 1995; Ziegler et al., 2000, for advantages of within-condition comparisons). Thus, the within-subject manipulation of prime exposure duration in both experiments allows us to obtain a comprehensive picture of masked identity priming effects--also including the examination of potential inhibitory effects of unrelated primes.

@@

\begin{figure}
\centering
\includegraphics{MaskedPriming_complete_mspg_files/figure-latex/hyp-mod-dat-figure-1.pdf}
\caption{\label{fig:hyp-mod-dat-figure}Mapping from hypotheses to data via evidence accumulation models. The bottom part of each graph represents sample paths, and the top part shows the cumulative density functions. From left to right: \emph{Null Effect} - there are no differences between the conditions; \emph{Effect in Encoding} - the difference between the conditions is on the encoding time, hence the RT distributions are shifted; and \emph{Effect of Encoding and Evidence Accumulation} - the differences between the conditions is on the rate of evidence accumulation, thus increasing the effect size for longer RTs (right-tail of the distribution).}
\end{figure}

@@

The pre-registration form for Experiment 1, together with the materials, data files, and R scripts can be found at \url{https://osf.io/57rzq/}.

@@

We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the \emph{brms} package (Bürkner, 2017, 2018) in R (R Core Team, 2021)\footnote{The full list of software we used for our analyses is as follows: R {[}Version 4.0.5; R Core Team (2021){]} and the R-packages \emph{bayestestR} {[}Version 0.9.0; Makowski et al. (2019){]}, \emph{brms} {[}Version 2.15.0; Bürkner (2017); Bürkner (2018){]}, \emph{dplyr} {[}Version 1.0.5; Wickham et al. (2021){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.3; Wickham (2016){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{patchwork} {[}Version 1.1.1; Pedersen (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{Rcpp} {[}Version 1.0.6; Eddelbuettel and François (2011); Eddelbuettel and Balamuta (2018){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{readxl} {[}Version 1.3.1; Wickham and Bryan (2019){]}, \emph{rworldmap} {[}Version 1.3.6; South (2011){]}, \emph{see} {[}Version 0.6.2; Lüdecke et al. (2020){]}, \emph{sp} {[}Version 1.4.5; Pebesma and Bivand (2005){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.1.0; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.3; Wickham (2021b){]}, \emph{tidyverse} {[}Version 1.3.0; Wickham et al. (2019){]}, \emph{tinylabels} (Barth, 2021), and \emph{xfun} {[}Version 0.22; Xie (2021){]}.}. We only analyzed trials where the target stimulus was a word. For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (5.77 \% of trials). For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (0.28 \% of trials). As the trials automatically ended after 2000 ms, there were no RTs longer than this. For both RTs and accuracy, we fitted a model with priming condition (unrelated vs.~identical) and prime duration (33.3 ms vs.~50 ms) as well as their interaction as the fixed effects. For the discrete predictors, we used contrasts as follows: For priming condition, identical was coded as -0.5 and unrelated was coded as 0.5. For priming duration, 33.3 ms was coded as -0.5 and 50 ms was coded as 0.5. We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items. We used the ex-Gaussian distribution to model response times, with both the mean of the Gaussian component \(\mu\) and the scale parameter of the exponential component \(\beta\) (equalling the inverse of the rate parameter \(\lambda\)) being allowed to vary between conditions. To model response accuracy, we used the Bernoulli distribution with a logit link. We used the default priors suggested by \emph{brms} except for the coefficients for the fixed effects, for which we applied weakly informative priors of \(\beta \sim N(0,100)\) in order to rule out improbably large effect sizes. Each model was fitted using four chains with 5000 iterations each with 1000 warmup iterations (10,000 iterations with 2000 warmup iterations for the accuracy models). We consider an effect as credible if the 95\% Credible Interval (CrI) estimated from the posterior distribution does not contain zero. In addition, to better visualize the distributional features of the latency data, we computed the delta plots for both priming and prime duration effects.

@@

\begin{tabular}{lllllllll}
\toprule
Stimulus Type & \multicolumn{1}{c}{Prime Duration} & \multicolumn{1}{c}{Relatedness} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{Median} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Accuracy}\\
\midrule
Nonword & 33.3 ms & Identity & 701 & 665 & 191 & 263 & 1,885 & 0.91\\
Nonword & 33.3 ms & Unrelated & 705 & 665 & 195 & 256 & 1,949 & 0.92\\
Nonword & 50 ms & Identity & 701 & 658 & 192 & 256 & 1,938 & 0.91\\
Nonword & 50 ms & Unrelated & 702 & 658 & 193 & 251 & 1,952 & 0.93\\
Word & 33.3 ms & Identity & 631 & 599 & 169 & 254 & 1,942 & 0.94\\
Word & 33.3 ms & Unrelated & 654 & 619 & 171 & 254 & 1,887 & 0.93\\
Word & 50 ms & Identity & 609 & 575 & 162 & 265 & 1,866 & 0.95\\
Word & 50 ms & Unrelated & 650 & 620 & 159 & 294 & 1,801 & 0.93\\
\bottomrule
\end{tabular}

@@

The RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 31.35, 95\% CrI {[}27.66, 35.01{]}), and higher in the 33.3 ms prime duration condition than in the 50 ms prime duration condition (\emph{b} = -11.38, 95\% CrI {[}-14.75, -8.02{]}). The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = 19.31, 95\% CrI {[}12.14, 26.46{]}). The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.01, 0.07{]}). However, the 50 ms prime exposure duration seems to be associated with a slightly lower \(\beta\), i.e., a slightly weaker right skew of the distribution, than the 33.3 ms condition (\emph{b} = -0.08, 95\% CrI {[}-0.12, -0.04{]}). On the other hand, there did not seem to be an interactive effect of prime relatedness and prime exposure time on the shape of the distribution (\emph{b} = 0.03, 95\% CrI {[}-0.05, 0.11{]}).

@@

\begin{tabular}{cccccc}
\toprule
Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
\midrule
Intercept ($\mu$) & 633.620 & 6.504 & 620.936 & 646.430 & 1.009\\
Intercept ($\beta$) & 4.669 & 0.031 & 4.607 & 4.729 & 1.003\\
Relatedness ($\mu$) & 31.353 & 1.878 & 27.659 & 35.006 & 1.001\\
Prime Duration ($\mu$) & -11.382 & 1.704 & -14.746 & -8.018 & 1.001\\
Relatedness:Prime Duration ($\mu$) & 19.309 & 3.699 & 12.141 & 26.455 & 1.000\\
Relatedness ($\beta$) & 0.032 & 0.020 & -0.007 & 0.070 & 1.000\\
Prime Duration ($\beta$) & -0.081 & 0.022 & -0.124 & -0.038 & 1.000\\
Relatedness:Prime Duration ($\beta$) & 0.029 & 0.041 & -0.052 & 0.110 & 1.000\\
\bottomrule
\addlinespace
\end{tabular}

@@

\begin{figure}
\centering
\includegraphics{MaskedPriming_complete_mspg_files/figure-latex/deltas-e1-words-1.pdf}
\caption{\label{fig:deltas-e1-words}Delta plots depicting the magnitude of the effect over time in Experiment 1. Each dot represents the mean RT at the .1, .3, .5, .7 and .9 quantiles. \emph{Panel A)} Difference in RT between unrelated and related trials for the 33.3 ms prime duration (left) and the 50 ms prime duration (right). \emph{Panel B)} Difference in RT between 50 ms and 33.3 ms prime duration trials for the identity (right) and the unrelated (left) conditions.}
\end{figure}

@@

The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (\emph{b} = -0.50, 95\% CrI {[}-0.71, -0.30{]}). The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33.3 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (\emph{b} = 0.20, 95\% CrI {[}-0.01, 0.42{]}). The interaction term indicates that the effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) was stronger in the 50 ms condition than the 33.3 ms condition (\emph{b} = -0.53, 95\% CrI {[}-0.94, -0.14{]}).

@@

\begin{tabular}{cccccc}
\toprule
Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
\midrule
Intercept & 3.451 & 0.122 & 3.217 & 3.695 & 1.000\\
Relatedness & -0.496 & 0.105 & -0.714 & -0.301 & 1.000\\
Prime Duration & 0.195 & 0.109 & -0.012 & 0.417 & 1.000\\
Relatedness:Prime Duration & -0.533 & 0.204 & -0.943 & -0.145 & 1.000\\
\bottomrule
\end{tabular}

@@

We analyzed the data in the same way as in Experiment 1, by only analyzing trials where the target stimulus was a word. For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (4.86 \% of trials). For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (0.08 \% of trials). For priming duration, 16.7 ms was coded as -0.5 and 33.3 ms was coded as 0.5. Otherwise, the model specifications were identical to those in Experiment 1.

@@

As in Experiment 1, the RT model indicates that the mean of the Gaussian component \(\mu\) was higher in the unrelated condition than the identical (\emph{b} = 8.80, 95\% CrI {[}5.42, 12.29{]}). For the main effect of prime duration, the CrI contains 0, suggesting that, when averaging across the relatedness conditions, there is no strong difference between the 16.7 ms and the 33.3 ms prime duration (\emph{b} = -3.48, 95\% CrI {[}-7.09, 0.16{]}). However, the interaction term demonstrates that this is actually due to the fact that there was a strong priming effect in the 33.3 ms condition, but only a negligible effect in the 16.7 ms condition (\emph{b} = 15.35, 95\% CrI {[}8.64, 22.05{]}). The shape parameter of the exponential component \(\beta\) was affected very little by prime relatedness (\emph{b} = 0.03, 95\% CrI {[}-0.01, 0.08{]}), prime exposure duration (\emph{b} = 0.01, 95\% CrI {[}-0.03, 0.06{]}), or their interaction (\emph{b} = -0.03, 95\% CrI {[}-0.12, 0.05{]}), suggesting that the shape of the RT distribution was not affected by the manipulations in Experiment 2.

@@

\begin{tabular}{cccccc}
\toprule
Parameter & \multicolumn{1}{c}{mean} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{lower bound} & \multicolumn{1}{c}{upper bound} & \multicolumn{1}{c}{$\hat{R}$}\\
\midrule
Intercept ($\mu$) & 658.462 & 9.372 & 640.004 & 676.606 & 1.002\\
Intercept ($\beta$) & 4.668 & 0.042 & 4.585 & 4.749 & 1.005\\
Relatedness ($\mu$) & 8.799 & 1.758 & 5.420 & 12.286 & 1.000\\
Prime Duration ($\mu$) & -3.481 & 1.841 & -7.095 & 0.161 & 1.000\\
Relatedness:Prime Duration ($\mu$) & 15.347 & 3.425 & 8.639 & 22.046 & 1.000\\
Relatedness ($\beta$) & 0.031 & 0.023 & -0.013 & 0.076 & 1.000\\
Prime Duration ($\beta$) & 0.013 & 0.022 & -0.030 & 0.055 & 1.000\\
Relatedness:Prime Duration ($\beta$) & -0.030 & 0.043 & -0.116 & 0.055 & 1.000\\
\bottomrule
\addlinespace
\end{tabular}
